Dimension Splitting and a Long Time-Step Multi-Dimensional Scheme for Atmospheric Transport

### 2017-05-25 revision/makeFigs/sbr_dx.tex
Hilary's first draft of revisions and replies to reviewer comments

\usepackage{babel}
\begin{document}
\begin{center}
\begin{tabular}{cc}
$\ell_{2}$ errors & $\ell_{\infty}$ errors\tabularnewline
\includegraphics[width=0.49\textwidth]{/mnt/homer2/hilary/latex/myPapers/YumengHilaryAdvectionPaper/revision/HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_plots_l2errors_dt} & \includegraphics[width=0.49\textwidth]{/mnt/homer2/hilary/latex/myPapers/YumengHilaryAdvectionPaper/revision/HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_plots_linferrors_dt}\tabularnewline
\end{tabular}
\par\end{center}
\end{document}

>>>>

\usepackage{babel}
\begin{document}
\begin{center}
\begin{tabular}{cc}
$\ell_{2}$ errors, convergence with $\Delta x$ for $c\approx1$ & $\ell_{\infty}$ errors, convergence with $\Delta x$ for $c\approx1$\tabularnewline
\includegraphics[width=0.49\textwidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_plots_l2errorsC1} & \includegraphics[width=0.49\textwidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_plots_linferrorsC1}\tabularnewline
$\ell_{2}$ errors, convergence with $\Delta x$ for $c\approx10$ & $\ell_{\infty}$ errors, convergence with $\Delta x$ for $c\approx10$\tabularnewline
\includegraphics[width=0.49\textwidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_plots_l2errorsC10} & \includegraphics[width=0.49\textwidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_plots_linferrorsC10}\tabularnewline
\end{tabular}
\par\end{center}
\end{document}

### 2017-05-25 revision/makeFigs/sbrc1.tex
Hilary's first draft of revisions and replies to reviewer comments

\usepackage{babel}
\begin{document}
\begin{center}
\begin{tabular}{cc}
$\ell_{2}$ errors, convergence with $\Delta x$ for $c\approx1$ & $\ell_{\infty}$ errors, convergence with $\Delta x$ for $c\approx1$\tabularnewline
\includegraphics[width=0.49\textwidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_plots_l2errorsC1} & \includegraphics[width=0.49\textwidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_plots_linferrorsC1}\tabularnewline
$\ell_{2}$ errors, convergence with $\Delta x$ for $c\approx10$ & $\ell_{\infty}$ errors, convergence with $\Delta x$ for $c\approx10$\tabularnewline
\includegraphics[width=0.49\textwidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_plots_l2errorsC10} & \includegraphics[width=0.49\textwidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_plots_linferrorsC10}\tabularnewline
\end{tabular}
\par\end{center}
\end{document}

>>>>

\usepackage{babel}
\begin{document}
\begin{tabular}{cc}
Orthogonal, dimensionally split scheme & Non-orthogonal, dimensionally split scheme\tabularnewline
\includegraphics[width=0.49\textwidth]{../YumengsGraphics/solidBodyRotationOnPlane_orthogonal_100x100_dt_1_Tcontours} & \includegraphics[width=0.49\textwidth]{../YumengsGraphics/solidBodyRotationOnPlane_nonOrthog_100x100_dt_1_Tcontours}\tabularnewline
Orthogonal, multi-dimensional scheme & Non-orthogonal, multi-dimensional scheme\tabularnewline
\includegraphics[width=0.49\textwidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_orthogonal_100x100_dt_1_Tcontours} & \includegraphics[width=0.49\textwidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_nonOrthog_100x100_dt_1_Tcontours}\tabularnewline
\multicolumn{2}{c}{\includegraphics[width=0.9\linewidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_legends_Tdiff}}\tabularnewline
\end{tabular}
\end{document}

### 2017-05-25 revision/makeFigs/sbrc10.tex
Hilary's first draft of revisions and replies to reviewer comments

\usepackage{babel}
\begin{document}
\begin{tabular}{cc}
Orthogonal, dimensionally split scheme & Non-orthogonal, dimensionally split scheme\tabularnewline
\includegraphics[width=0.49\textwidth]{../YumengsGraphics/solidBodyRotationOnPlane_orthogonal_100x100_dt_1_Tcontours} & \includegraphics[width=0.49\textwidth]{../YumengsGraphics/solidBodyRotationOnPlane_nonOrthog_100x100_dt_1_Tcontours}\tabularnewline
Orthogonal, multi-dimensional scheme & Non-orthogonal, multi-dimensional scheme\tabularnewline
\includegraphics[width=0.49\textwidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_orthogonal_100x100_dt_1_Tcontours} & \includegraphics[width=0.49\textwidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_nonOrthog_100x100_dt_1_Tcontours}\tabularnewline
\multicolumn{2}{c}{\includegraphics[width=0.9\linewidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_legends_Tdiff}}\tabularnewline
\end{tabular}
\end{document}

>>>>

\usepackage{babel}
\begin{document}
\begin{tabular}{cc}
Orthogonal, dimensionally split scheme & Non-orthogonal, dimensionally split scheme\tabularnewline
\includegraphics[width=0.49\textwidth]{../YumengsGraphics/solidBodyRotationOnPlane_orthogonal_100x100_dt_10_TcontoursBig} & \includegraphics[width=0.49\textwidth]{../YumengsGraphics/solidBodyRotationOnPlane_nonOrthog_100x100_dt_10_TcontoursBig}\tabularnewline
Orthogonal, multi-dimensional scheme & Non-orthogonal, multi-dimensional scheme\tabularnewline
\includegraphics[width=0.49\textwidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_orthogonal_100x100_dt_10_TcontoursBig} & \includegraphics[width=0.49\textwidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_nonOrthog_100x100_dt_10_TcontoursBig}\tabularnewline
\multicolumn{2}{c}{\includegraphics[width=0.9\linewidth]{../HilarysGraphics/multiDadvectCases_solidBodyRotationOnPlane_legends_TdiffBig_Tdiff}}\tabularnewline
\end{tabular}
\end{document}
